\Large{Adversarial Variational Optimization of Non-Differentiable Simulators}

### 2017-07-22 tex/paper.tex

We can view the optimization of the marginal likelihood with respect to $\bfpsi$ through the lens of empirical Bayes (EB), where the data are used to optimize a prior within the family $q(\bftheta|\bfpsi)$. If $\rho$ is the KL distance, $\bfpsi^*$ would correspond to the maximum marginal likelihood estimator advocated by Rubin~\citep{rubin1984}.
When $\rho$ is the Wasserstein distance, $\bfpsi^*$ is referred to as the
minimum Wasserstein estimator (MWE). 
When the model is well specified, the MWE
coincides with the true data-generating parameter; however, if the model is
misspecified, the MWE is typically different from the maximum likelihood
estimator (MLE).
Moreover, if the simulator $p(\bfx |
\bftheta)$ is misspecified, $q(\bftheta | \bfpsi)$ will attempt to smear it so that the marginal
model $q(\bfx | \bfpsi)$ is closer to $p_r(\bfx)$. However, if the simulator is well specified, 
then $q(\bftheta | \bfpsi)$ will concentrate its mass around the true data-generating parameter.

>>>>

We can view the optimization of the marginal likelihood $q(\bfx | \bfpsi)$ with respect to $\bfpsi$ through the lens of empirical Bayes (EB), where the data are used to optimize a prior within the family $q(\bftheta|\bfpsi)$. If $\rho$ is the KL distance, $\bfpsi^*$ would correspond to the maximum marginal likelihood estimator advocated by Rubin~\citep{rubin1984}.
When $\rho$ is the Wasserstein distance, $\bfpsi^*$ is referred to as the
minimum Wasserstein estimator (MWE). 
When the model is well specified, the MWE
coincides with the true data-generating parameter; however, if the model is
misspecified, the MWE is typically different from the maximum likelihood
estimator (MLE).
Thus, if the simulator $p(\bfx |
\bftheta)$ is misspecified, $q(\bftheta | \bfpsi)$ will attempt to smear it so that the marginal
model $q(\bfx | \bfpsi)$ is closer to $p_r(\bfx)$. However, if the simulator is well specified, 
then $q(\bftheta | \bfpsi)$ will concentrate its mass around the true data-generating parameter.
